Robotic Cart System

### 2021-04-06 parts/10-introduction.tex
Update 10-introduction.tex

%----------------------------------------------------------------------
\section{Problem Statement}
%----------------------------------------------------------------------
Helicopters are of a paramount importance as
they are used in many civilian and military applications due to their ability for vertical take-off and landing. To enable their use in such applications, intensive research has been conducted to date since helicopters involve complex nonlinear dynamics. Most of the work on helicopter based research requires dedicated computers for controlling their motion to specific configurations and resistant to turbulent conditions. Such methods are expensive and time-consuming to develop. Implementation of motion control techniques using cost-effective hardware is still a challenge.

In this project, we are proposing an algorithm for smart control of a team of two degree-of freedom (two-DOF) helicopters using conventional motion control in cooperation with machine learning techniques where a user will be able to configure helicopters from any initial position. Even though conventional techniques have been tested with simple platforms in the literature, the current project employs conventional motion control strategies in cooperation with machine learning technique (reinforcement learning, for instance) for a team of helicopters as well as introducing user control via mobile devices. This project is expected to encourage research in this area as well as serve as an educational tool in teaching environments.

%----------------------------------------------------------------------
\section{Literature Review}
%----------------------------------------------------------------------
Our project requires a great deal of research as some of our tasks have not been attempted before.  As a result, we have examined research papers, work complete by other projects at Bradley University, and documentation/teaching materials from Quanser Inc.

Among the major challenges in developing unmanned systems is to implement a modular, cost-effective, and robust teleoperation system, where the motion of a group of helicopters is controlled by mobile devices. In some cases, computer simulations are conducted to reveal the performance control structures of a 2-DOF helicopter~\cite{DArpino2010}. A large body of research has been conducted in the literature to focus on developing different control structures, such as linear-quadratic regulators (LQR)/Gaussian (LQG), sliding-mode controls (SMC), and advance nonlinear controls, that are specifically applied to 2-DOF helicopters. See~\cite{Subramanian2016-Robust,Ahmed2010-Sliding}, for example, and some references therein. Furthermore,  soft-computing tools, such as fuzzy-logic, neural networks, and a few combinations of them are employed for controlling the motion of a 2-DOF helicopter~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy,Gao2016-DataDriven,Hernandez2012-Decentralized}.

The documentation of Quanser AERO\footnote{See \href{https://www.quanser.com/}{https://www.quanser.com/} for details} employs LQR and LQG motion control techniques for teaching purposes.  This involves creating a linearized system model to calculate the LQR state-feedback gain.  A model reference adaptive control (MARC) scheme using Lyapunov functions has been used by~\cite{Subramanian2016-Robust} for adaptive motion control of a 2-DOF helicopter.  SMC is a nonlinear control technique to drive the system states onto a surface in the state space.  This method has been used  by~\cite{Ahmed2010-Sliding}.  Fuzzy-logic controllers use an inference engine to produce an output as used in~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy}.  The ADP technique does not rely on knowledge of the system model.  Instead, it uses data to reconstruct the states as preformed by~\cite{Gao2016-DataDriven}.  Authors in~\cite{Hernandez2012-Decentralized} used high order neural networks (HONN) to approximate non-linearities in the system model.

As can be noticed, most of the motion control techniques are either tested using computer simulations or use dedicated computational platforms, that may not be modular and/or cost-effective, for developing motion control algorithms. This is due to the fact that the aforementioned techniques are mainly to propose novel motion control techniques and not focused on hardware implementation platforms. Therefore, the current work considers implementing a conventional motion control technique using modular and cost-effective hardware platforms in the context of a teleoperation system, where a human operator has the ability to control the motion of a team of helicopters using a smart mobile device.

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organised into 6 chapters.  Chapter \ref{ch: Chapter1} discusses what this project hopes to accomplish and what similar projects have completed.  Chapter \ref{ch: Chapter2} explains how to create a mathematical model for the system.  Chapter \ref{ch: Chapter3} provides a breif explanation of the control algorithms and architectures used.  Chapter \ref{ch: Chapter4} contains the results from our simulations.  Chapter \ref{ch: Chapter5} disucsses results from USB, Raspberry Pi, and Mobile Device implementation.  Chapter \ref{ch: Chapter6} concludes the paper and provides insight into future directions.

>>>>

%----------------------------------------------------------------------
\section{Problem Statement}
%----------------------------------------------------------------------
Robotic carts are a prevalent invention designed to aid users in a number of important indoor and outdoor tasks. There are robotic systems currently available in the market that perform these tasks in a variety of ways. For example, in a grocery store, a customer may require the need of more than one cart but cannot push or pull two carts simultaneously. One major drawback, however, is that people with disabilities cannot push one cart let alone have a second cart to carry more items. Moreover, robots used for this purpose are more costly than they are worth. In this project, we are proposing a robotic cart that would primarily use analog signals with the use of cost-effective wireless communication to identify the customer and be able to track and follow the customer through the store. The implementation of such a fully functional robotic cart will outreach the scope of the project but is the overall goal for this project in the coming years while encouraging further research in this field. Applications of the proposed robotic cart include, but are not limited to, delivery carts to follow mail personnel and carry the deliveries, file transfer carts in offices, hospital carts to aid nurses and doctors by carrying medicine or surgery supplies, and carts in construction sites to carry tools and other supplies across the job site.

%----------------------------------------------------------------------
\section{Literature Review}
%----------------------------------------------------------------------
Abundant research in the field of mobile robotics shows various ways to develop robotic carts that will help consumers in carrying groceries through stores. See~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}, for example. Currently, the work being done focuses on a few different methods of having a robotic cart interface with the customer and follow them through the store.

\vspace*{12pt}
\noindent
One such method that has been utilized to make a cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}. Another method that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow them through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}. Therein, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.

\vspace*{12pt}
\noindent
In the current project, we are implementing XBee S2C RF radios, which are inexpensive and easily configurable, as a remote target device that is carried by the user. The robot will be able to track this remote instead of using line of sight methods~\cite{Miah2018-Intelligent}. In addition to the XBee S2C RF radios, we will equip the robot with a parabolic reflector, which improves Wi-Fi reception at various distances and angles, \textit{i.e.,} angle of arrivals of RF signals from the remote, based on research done previously in this type of robot localization and mapping~\cite{Miah2018-Intelligent}~\cite{Li2013ANA}.

\vspace*{12pt}
\noindent
The approach using signal strength of RF signals also requires an understanding of multipath interference which is common in Wi-Fi based wireless positioning sensing systems. Authors in~\cite{xie_jiang_zhao_zhang_2019} explain that using course estimation calculations such as received signal strength indicator (RSSI) and time difference of arrival (TDoA) is key to compensate for the multipath interference in received signals. The work in ~\cite{ladd_bekris_rudys_kavraki_wallach_2005} shows a different approach to the multipath issue by using an IEEE 802.11b wireless ethernet device to measure RF signals. This device system was used because it is communicable between a mobile device and a localization based service with low complexity for the user. Also, in~\cite{lindhe_johansson_bicchi_2007}, the research states several other ways to counteract the multipath fading with methods such as antenna diversity, frequency spreading, or adaptive antenna arrays. The method used in this paper was to sample the radio signal strength (RSS) at discrete points without too much deviation from the robot's desired position in an indoor environment. Lastly, in~\cite{Lindhe2009} the method that is utilized exploits multipath fading by measuring the signal-to-noise ratio (SNR) and adjusting the robot's motion to spend more time where the channel strength is greater.

\vspace*{12pt}
\noindent
All of the solutions that were found required direct line-of-sight between the robot and the user. In this project we aim to use the XBee S2C RF radios and a parabolic reflector combined into a rotating system similar to the one presented in~\cite{Miah2018-Intelligent} in order to have the robot track the customer through a store without using line-of-sight sensing. The major challenge of this implementation will be estimating the distance between the robot and the remote in varying environments.

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organised into the following 6 chapters:

\begin{itemize}
	\item Chapter \ref{ch: Chapter1} discusses the background and goals of our project and what other similar projects have accomplished
	\item Chapter \ref{ch: Chapter2} explains how our robotic cart system is broken down fundamentally and the system components we used to build the robot
	\item Chapter \ref{ch: Chapter3} goes over the design of our parabolic reflector arrays and how we set them up on the robot
	\item Chapter \ref{ch: Chapter4} provides an explanation of the algorithms we used to create the code to make the robot move
	\item Chapter \ref{ch: Chapter5} discusses the implementation of all the parts onto the robot and our experimental results we got when running the robot
	\item Chapter \ref{ch: Chapter6} concludes our project work and discusses future endeavors on this project
\end{itemize}
